Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-12-11 demystify.tex
updates

\chapter{Interview and the Waiting Game}\label{chap:interview}
\chapterinfo{Getting an interview is typically a \emph{good sign}; but no interview does not mean rejection}

@@

\part{Funding}\label{part:funding}
\chapter{Funding}\label{sec:funding}
\chapterinfo{TAs, RAs, and fellowships are main funding sources for PhDs.  TAs are provided by the department to help with classes. RAs are given by profs. to help with their research.  Fellowships, provided by the university, department, or external sources such as government or industry, give move flexibility but can be very competitive.}

@@

\chapterinfo{Not every university has PhD progarms in CS. Not every professor, even those in CS, can advise or graduate CS PhD students.}

@@

\section{Are profs. so busy that they completely ignore emails?} \label{sec:busy}

>>>>

\part{After You Apply}\label{part:after-apply}
\chapter{Interview and the Waiting Game}\label{chap:interview}
\chapterinfo{Getting an interview is typically a \emph{good sign}; but no interview does not mean rejection}

@@

\part{Funding, Schools, and Profs.}\label{part:funding-schools-profs}

\chapter{Funding}\label{sec:funding}
\chapterinfo{TAs, RAs, and fellowships are main funding sources for PhDs.  TAs are provided by the department to help with classes. RAs are given by profs. to help with their research.  Fellowships, provided by the university, department, or external sources such as government or industry, give move flexibility but can be very competitive.}

@@

\chapterinfo{Not every university has a CS PhD program. Not every professor, even those in CS, can advise or graduate CS PhD students.}

@@

\subsection{Are profs. so busy that they completely ignore emails?}\label{sec:busy}
